### 2014-10-27 motivation.tex

Although it is easy to understand the reasons behind the occurrence of the
aforementioned negative balance and missing update anomalies, the fix is not
quite apparent. Making \cf{getBalance} a strongly consistent operation is
definitely sufficient to avert anomalies, but is it really necessary? Given
that a strongly consistent operation is significantly expensive, both in terms
of availability and monetary overheads~\cite{DynamoDB,Pileus}, we ideally would
not want to request strong consistency, unless there are no alternatives
available. Unfortunately, this requires us to understand subtle differences in
semantics of various kinds of weak consistency alternatives, offered by the
data stores.

@@

\subsection{From contracts to implementation}

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{Graphs/BankAccount_Th_vs_Lat}
\caption{Bank Account: Throughput vs Latency. Quelea is our implementation.
Strong and Quelea are correct. High. Avail. and causal are incorrect (withdraw
not strong). 20\% withdraw, 20\% deposit, 60\% getBalance.}
\label{grf:BankAcc_Th_vs_Lat}
\end{figure}

Although it is easy to understand the reasons behind the occurrence of the
aforementioned negative balance and missing update anomalies, the fix is not
quite apparent. Making \cf{getBalance} a strongly consistent operation is
definitely sufficient to avert anomalies, but is it really necessary? Given
that a strongly consistent operation is significantly expensive
(Figure~\ref{grf:BankAcc_Th_vs_Lat} \KC{Should I include the numbers here? If
yes, I'll expand the text.}), both in terms of availability and monetary
overheads~\cite{DynamoDB,Pileus}, we ideally would not want to request strong
consistency, unless there are no alternatives available. Unfortunately, this
requires us to understand subtle differences in semantics of various kinds of
weak consistency alternatives, offered by the data stores.

@@

\subsection{From Contracts to Implementation}
